Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-08-03 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] christoph's corrections to finalize draft for arxiv v1 submission

% references to ...
\def \refeq#1{(\ref{#1})}
\def \refsec#1{Section \ref{#1}}
\def \refapp#1{\ref{#1}}
\def \reffig#1{Figure \ref{#1}}
\def \reftab#1{Table \ref{#1}}

@@

%%
%% Comments
%%
\newcommand{\fred}[1]{{\color{green}{#1}}}
\newcommand{\todo}[1]{{\color{magenta}{ {\bf ToDo: }{#1}}}}
\newcommand{\checked}[1]{{\color{brown}{ {\bf Checked: }{#1}}}}
\renewcommand{\checked}[1]{#1}

@@

\thankstext[$\star$]{t1}{\todo{EOS-2015-??}, FLAVOUR(267104)-ERC-107}
\thankstext{e1}{e-mail: frederik.beaujean@lmu.de}
\thankstext{e2}{e-mail: christoph.bobeth@ph.tum.de}
\thankstext{e3}{e-mail: sjahn@mpp.mpg.de}

@@

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  depends on two parameters, the lepton forward-backward asymmetry, $A_{\rm
    FB}^\ell$, and the flat term, $F_H^\ell$. Both are strongly suppressed in
  the standard model and constitute sensitive probes of tensor and scalar
  contributions. We use the latest experimental results for $\ell = \mu$ in
  combination with $B_s\to \bar\mu\mu$ to derive the strongest model-independent
  bounds on tensor and scalar effective couplings to date. The measurement of
  $F_H^\mu$ is complementary to that of the branching ratio of $B_s\to
  \bar\mu\mu$ and allows us---for the first time---to constrain all
  complex-valued (pseudo-)scalar couplings and their chirality-flipped
  counterparts in one fit. Based on Bayesian fits of various scenarios, we find
  that our bounds even become tighter when vector couplings are allowed to
  deviate from the standard model and that specific combinations of angular
  observables in $B \to K^*$ are still allowed to be up to two orders of
  magnitude larger than in the standard model, which would place them in the
  region of LHCb's sensitivity.
%   \todo{check captions of figures and tables}
\end{abstract}

@@

With the analysis of the data collected by the LHCb Collaboration
during phase I at the Large Hadron Collider (LHC), we now have access
to rather large samples of rare $B$ meson decays with branching ratios
below $10^{-5}$. As a consequence, angular analyses of three- and
four-body final states can be used to measure a larger number of
observables than previously possible at the B factories BaBar and
Belle. In this work we focus on rare $B$ decays driven at the parton
level by the flavor-changing neutral-current (FCNC) transition $b\to s
\bar\ell\ell$ that constitutes a valuable probe of the standard model
(SM) and provides constraints on its extensions.

@@

Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
factors for vector and dipole couplings present in the SM, thereby enhancing
their sensitivity to tensor and scalar couplings \cite{Bobeth:2007dw,
  Bobeth:2012vn}. A similar enhancement of scalar couplings compared to
helicity-suppressed vector couplings of the SM is well-known from $B_s\to
\bar\mu\mu$. Unfortunately the limited data set of $B\to K^*(\to K\pi)
\bar\ell\ell$ from LHCb \cite{Aaij:2013qta} did not allow to perform a full
angular analysis without the assumption of vanishing scalar and tensor couplings
in this decay mode. In the future with more data or special-purpose analysis
techniques like the method of moments~\cite{beaujean:2015mom}, certain angular
observables in $B\to K^* \bar\ell\ell$ will provide additional constraints on
such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz} and the
linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as the experimental test of the
relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn} at low
hadronic recoil.

@@

In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory
\begin{equation}
  \label{eq:Heff}
\begin{aligned}
  {\cal L}_{\rm eff}  =
   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, & V_{tb}^{} V_{ts}^\ast
      \, \Big[ C_7 \Op_7 + C_{7'} \Op_{7'}
 \\ & +
       \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i \Big] + \text{h.c.}
\end{aligned}
\end{equation}
the most general dimension-six flavor-changing operators $\Op_i$ mediating $b\to
s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their chiral
structure. There are dipole ($i = 7,7'$ \fred{so there is no $\mu, \tau$ version
  of $\wilson{7}$? I guess it should also depend on $\mu_b$}) and vector ($i =
9,9',10,10'$) operators
\begin{equation}
  \label{eq:SM:ops}
\begin{aligned}
  \Op_{7(7')} &
  = \frac{m_b}{e}\!\[\bar{s} \sigma^{\mu\nu} P_{R(L)} b\] F_{\mu\nu}\,,
\\
  \Op_{9(9')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
\\[0.1cm]
  \Op_{10(10')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
further scalar ($i = S,S',P,P'$) operators
\begin{equation}
  \label{eq:scalar:ops}
\begin{aligned}
  \Op_{S(S')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
\\[0.1cm]
  \Op_{P(P')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
and tensor ($i = T,T5$) operators
\begin{equation}
  \label{eq:tensor:ops}
\begin{aligned}
  \Op_{T} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
\\[0.1cm]
  \Op_{T5} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
where the notation $\Op_{T5} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
\[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
also used frequently in the literature. The respective short-distance couplings,
the Wilson coefficients $\wilson[\ell]{i}(\mu_b)$ are evaluated at a scale of
the order of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM
predictions in the presence of new physics.

@@

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with $\mbox{dim} > 6$. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}\,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.  The flat
term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed away from both \fred{Why
  both? At $q^2_{\rm max}$ it is strongly suppressed according to the formula
  given.} kinematic endpoints in $q^2$, except for $\ell = \tau$,
\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  Nonzero values of
$A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
which will modify the simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
available for this source of SM background\footnote{The leading QED corrections
  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
  corresponding effects in $B\to K \bar\ell\ell$.}.

@@

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \begin{center}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \end{center}
  \caption{ The sensitivity to the tensor coupling $\mbox{Re}(\wilson{T})$ of
    $F_H$ (first row) and ${\cal B}$ (second row) in $B^+ \to K^+ \bar\mu\mu$
    and ${\cal B}$ (third row), $J_{1c} + J_{2c}$ (fourth row), and $J_{1s}-3
    J_{2s}$ (fifth row) in $B^0 \to K^{*0} \bar\mu\mu$ integrated over low- and
    high-$q^2$ bins. In the last two rows, the observables are rescaled by the
    lifetime of the $B$ meson for easier comparison with the branching
    ratios. The bands represent the theory uncertainties at 68\% and 95\%
    probability of the prior predictive distribution.  For comparison, two sets
    of bands are shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
    $\wilson[NP]{9} = -1.1$ (red), and an additional band of the latest 68\%
    confidence interval reported by LHCb (grey) if a measurement is
    available. \checked{} }
  \label{fig:FHvsCT}
\end{figure*}

@@

From \reffig{fig:FHvsCT}, the highest sensitivity to tensor couplings of any $B
\to K$ observable is attained by $F_H^\ell$ at high $q^2$ due to a partial
cancellation of form factors \cite{Bobeth:2012vn}. If the experimental
uncertainty could be reduced further, $F_H^\ell$ would give a very strong
constraint on a simultaneous negative shift in $\wilson[NP]{9}$ and
$\wilson[NP]{T}$. The prediction of ${\cal B}(B\to K \bar\ell\ell)$ is
essentially insensitive to $\wilson{T}$ but sensitive to $\wilson{NP}[9]$. A
stronger impact on global fits, however, would required reduced theory
uncertainty.

The observable ${\cal B}(B\to K^* \bar\ell\ell)$ shows moderate dependence on
$\wilson{T}$ at least at low $q^2$ and has some impact on the constraints on
tensor couplings as will be discussed in \refsec{sec:results}. At the moment,
theory and experimental uncertainty are of similar size.

$J_{1c}+J_{2c}$ is sensitive to $\wilson{T}$ in both $q^2$ regimes. At low
$q^2$, it is mildly affected by $\wilson[NP]{9}$, whereas at high $q^2$ it is
unaffected. Regarding $J_{1s}-3J_{2s}$, the situation is reversed: here the
strong dependence on $\wilson{T}$ appears at low $q^2$.  Overall, $F_H^\ell$,
$J_{1c}+J_{2c}$ at large $q^2$, and $J_{1s}-3J_{2s}$ are sensitive to
$\wilson{T}$ and theoretically very clean around $\wilson{T}=0$.

From the available measurements, $F_H^\ell$ at high $q^2$ currently provides the
most stringent constraints on the size of tensor couplings. Moreover, the
dependence on vector couplings is such that $\wilson[NP]{9} < 0$ leads to
stronger constraints on $\wilson{T}$ than $\wilson[NP]{9} \approx
0$.

@@

Eventually we also explore the effect of interference with NP in the vector
couplings $\wilson{9,\,9',\,10,\,10'}$ on the bounds on tensor and scalar
couplings.  For this purpose we include also the branching ratio, the lepton
forward-backward asymmetry, and the rate CP asymmetry of $B\to K^* \bar\mu\mu$
as they provide additional constraints on the real and imaginary parts of
$\wilson{9,\,9',\,10,\,10'}$. The experimental inputs of all observables
entering our fits is listed in \reftab{tab:observables} together with input for
the $B\to K^{(*)}$ form factors. More details on the latter can be found in
\refapp{app:theory:inputs}.

@@

There are no discrepancies between the latest measurements for $\ell = \mu$
(throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ in $B^+ \to K^+
\bar\mu\mu$ and their tiny SM predictions; cf. \reffig{fig:FHvsCT}. Thus our
main objective is to derive constraints on tensor and scalar couplings through
the enhanced sensitivity of both observables to those couplings compared to
vector couplings. For this purpose, we will consider several model-independent
scenarios, progressing from rather restricted to more general ones in order to
asses the effect of cancellations due to interference of various contributions.

For each coupling we vary in a fit, we remain as general as possible, treat it
as a complex number and use the cartesian parametrization assuming uniform
priors for ease of comparison with previous studies. Specifically, we set
\begin{align}
  \label{eq:wilson-prior}
  \mbox{Re}(\wilson{S,S',P,P',T,T5}) &\in [-1, 1],\nn \mbox{Re}(\wilson{9,9',10,10'}) &\in [-7, 7],
\end{align}
and the same for the imaginary parts. The priors of the nuisance parameters are given in \refapp{app:theory:inputs}.

We start with the scenario of only tensor couplings and see that they are well
constrained by $F_H^\mu$ alone. In a second scenario we consider only scalar
couplings in order to investigate the complementarity of $F_H^\mu$ and $B_s \to
\bar\mu\mu$. Here we find that---for the first time---all complex-valued scalar
couplings can be bounded simultaneously by the combination of both
measurements. Finally we consider as a special scenario the SM augmented by
dimension six operators as an effective theory of new physics below some high
scale $\Lambda_{\rm NP}$ assumed much larger than the typical scale of
electroweak symmetry breaking. In addition, the model contains one scalar
doublet under $SU(2)_L$ as in the SM. For each scenario, we also investigate
interference effects with new physics in vector couplings. Finally, we conclude
this section with posterior predictions---conditional on all experimental
constraints---of the probable ranges of the not-yet-measured angular observables
in $B\to K^*\bar\mu\mu$ and $A_{\Delta\Gamma}$ in $B_s\to\bar\mu\mu$.

@@

In a scenario with only tensor complex-valued couplings $\wilson{T,\, T5}$, the
experimental measurement of $F_H^\mu$ constrains the combination $|\wilson{T}|^2
+ |\wilson{T5}|^2$, up to some small interference of $\wilson{T}$ with vector
couplings $\wilson{7,\,7',\,9,\,9'}$; cf. \refeq{eq:FH-dependence}.  The
according 68\% (95\%) 1D-marginalized probability intervals are listed in the
second column of \reftab{tab:cTT5:1-dimCLs}. From the third column, it is seen
that the constraints become tighter when utilising all observables in
\reftab{tab:observables}, mainly due to the sensitivity of the branching ratio
of $B\to K^{*} \bar\mu\mu$ to tensor couplings (see also
\reffig{fig:FHvsCT}). The latter stronger bounds are driven by the new lattice
results of $B\to K^*$ form factors that predict values above the measured
values~\cite{Horgan:2013pva}. Since tensor couplings contribute constructively
to ${\cal B}(B\to K^{*}\bar\mu\mu)$, large values are better constrained. In
this scenario with vanishing scalar couplings, current measurements of $A_{\rm
  FB}^\mu(B^+\to K^+\bar\mu\mu)$ barely provide any constraint;
cf.~\refeq{eq:AFB-dependence}.

>>>>

% references to ...
\def \refeq#1{(\ref{#1})}
\def \refsec#1{Section~\ref{#1}}
\def \refapp#1{\ref{#1}}
\def \reffig#1{Figure~\ref{#1}}
\def \reftab#1{Table~\ref{#1}}

@@

%%
%% Comments
%%
\newcommand{\christoph}[1]{{\color{red}{#1}}}
\newcommand{\fred}[1]{{\color{green}{#1}}}
\newcommand{\todo}[1]{{\color{magenta}{ {\bf ToDo: }{#1}}}}
\newcommand{\checked}[1]{{\color{brown}{ {\bf Checked: }{#1}}}}
\renewcommand{\checked}[1]{#1}

@@

\thankstext[$\star$]{t1}{\christoph{Preprint: EOS-2015-03,} FLAVOUR(267104)-ERC-107}
\thankstext{e1}{e-mail: frederik.beaujean@lmu.de}
\thankstext{e2}{e-mail: christoph.bobeth@ph.tum.de}
\thankstext{e3}{e-mail: sjahn@mpp.mpg.de}

@@

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  depends on two parameters, the lepton forward-backward asymmetry, $A_{\rm
    FB}^\ell$, and the flat term, $F_H^\ell$. Both are strongly suppressed in
  the standard model and constitute sensitive probes of tensor and scalar
  contributions. We use the latest experimental results for $\ell = \mu$ in
  combination with $B_s\to \bar\mu\mu$ to derive the strongest model-independent
  bounds on tensor and scalar effective couplings to date. The measurement of
  $F_H^\mu$ \christoph{provides complementary constraints} to that of the branching ratio of $B_s\to
  \bar\mu\mu$ and allows us---for the first time---to constrain all
  complex-valued (pseudo-)scalar couplings and their chirality-flipped
  counterparts in one fit. Based on Bayesian fits of various scenarios, we find
  that our bounds even become tighter when vector couplings are allowed to
  deviate from the standard model and that specific combinations of angular
  observables in $B \to K^*$ are still allowed to be up to two orders of
  magnitude larger than in the standard model, which would place them in the
  region of LHCb's sensitivity.
\end{abstract}

@@

With the analysis of the data collected by the LHCb Collaboration
during \christoph{Run} I at the Large Hadron Collider (LHC), we now have access
to rather large samples of rare \christoph{$B$-meson} decays with branching ratios
below $10^{-5}$. As a consequence, angular analyses of three- and
four-body final states can be used to measure a larger number of
observables than previously possible at the B factories BaBar and
Belle. In this work we focus on rare $B$ decays driven at the parton
level by the flavor-changing neutral-current (FCNC) transition $b\to s
\bar\ell\ell$ that constitutes a valuable probe of the standard model
(SM) and provides constraints on its extensions.

@@

Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
factors for vector and dipole couplings present in the SM, thereby enhancing
their sensitivity to tensor and scalar couplings \cite{Bobeth:2007dw,
  Bobeth:2012vn}. A similar enhancement of scalar couplings compared to
helicity-suppressed vector couplings of the SM is well-known from $B_s\to
\bar\mu\mu$. Unfortunately the limited data set of $B\to K^*(\to K\pi)
\bar\ell\ell$ from LHCb \cite{Aaij:2013qta} \christoph{did not yet} allow to perform a full
angular analysis without the assumption of vanishing scalar and tensor couplings
in this decay mode. In the future with more data or special-purpose analysis
techniques like the method of moments~\cite{beaujean:2015mom}, certain angular
observables in $B\to K^* \bar\ell\ell$ will provide additional constraints on
such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz} and the
linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as the experimental test of the
relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn} at low
hadronic recoil.

@@

In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory
\begin{equation}
  \label{eq:Heff}
\begin{aligned}
  {\cal L}_{\rm eff}  =
   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, & V_{tb}^{} V_{ts}^\ast
      \, \Big[ \christoph{C_7(\mu_b) \Op_7 + C_{7'}(\mu_b) \Op_{7'}}
 \\ & +
       \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i \Big] + \text{h.c.}
   \christoph{\,,}
\end{aligned}
\end{equation}
the most general dimension-six flavor-changing operators $\Op_i$ mediating $b\to
s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their chiral
structure. There are dipole ($i = 7,7'$) and vector ($i = 9,9',10,10'$) operators
\begin{equation}
  \label{eq:SM:ops}
\begin{aligned}
  \Op_{7(7')} &
  = \frac{m_b}{e}\!\[\bar{s} \sigma^{\mu\nu} P_{R(L)} b\] F_{\mu\nu}\,,
\\
  \Op_{9(9')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
\\[0.1cm]
  \Op_{10(10')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
further scalar ($i = S,S',P,P'$) operators
\begin{equation}
  \label{eq:scalar:ops}
\begin{aligned}
  \Op_{S(S')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
\\[0.1cm]
  \Op_{P(P')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
and tensor ($i = T,T5$) operators
\begin{equation}
  \label{eq:tensor:ops}
\begin{aligned}
  \Op_{T} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
\\[0.1cm]
  \Op_{T5} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
where the notation $\Op_{T5} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
\[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
also used frequently in the literature. The respective short-distance couplings,
the Wilson coefficients $\wilson[(\ell)]{i}(\mu_b)$ are evaluated at a scale of
the order of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM
predictions in the presence of new physics.

@@

\christoph{For the rest of this article we will suppress the lepton-flavor index
on the Wilson coefficients: $\wilson[\ell]{i} \to \wilson[]{i}$. In \refsec{sec:results}
we exploit data with $\ell =\mu$ only, hence all derived constraints apply in
principle only to the muonic case, but can be carried over to other lepton
species $\ell = e,\, \tau$ in cases of NP models that do not violate lepton
flavor. In general the Wilson coefficients are decomposed into SM and NP
contributions $\wilson[]{i} = \wilson[SM]{i} + \wilson[NP]{i}$, but often we
will use $\wilson[]{i}$ for Wilson coefficients with zero (or suppressed) SM 
contributions synonymously for $\wilson[NP]{i}$. }

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with \christoph{$\mbox{dim} \geq 8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2} 
    \christoph{\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests. 
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed \christoph{by small 
lepton masses for the considered kinematical region $1 \leq q^2 \leq 22$ GeV$^2$}
\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  
Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED 
corrections, which will modify the simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
available for this source of SM background\footnote{The leading QED corrections
  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} \todo{(update ref. with published)} might provide an estimate of
  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's comment?!}

@@

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \begin{center}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \end{center}
  \caption{ The sensitivity to the tensor coupling $\mbox{Re}(\wilson{T})$ of
    \christoph{$F_H^\mu$} (first row) and \christoph{${\cal B}_\mu$} (second row) 
    in $B^+ \to K^+ \bar\mu\mu$
    \christoph{as well as} \christoph{${\cal B}_\mu$} (third row), $(J_{1c} + J_{2c})$ 
    (fourth row), and $(J_{1s}-3 J_{2s})$ (fifth row) in $B^0 \to K^{*0} \bar\mu\mu$ 
    integrated over low- and high-$q^2$ bins. In the last two rows, the observables 
    are rescaled by the
    lifetime of the $B$ meson for easier comparison with the branching
    ratios. The bands represent the theory uncertainties at 68\% and 95\%
    probability of the prior predictive distribution.  For comparison, two sets
    of bands are shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
    $\wilson[NP]{9} = -1.1$ (red), and an additional band of the latest 68\%
    confidence interval reported by LHCb (grey) if a measurement is
    available. \checked{} }
  \label{fig:FHvsCT}
\end{figure*}

@@

From \reffig{fig:FHvsCT}, the highest sensitivity to tensor couplings of any $B
\to K$ observable is attained by \christoph{$F_H^\mu$} at high $q^2$ due to a partial
cancellation of form factors \cite{Bobeth:2012vn}. If the experimental
uncertainty could be reduced further, \christoph{$F_H^\mu$} would give a very strong
constraint on a simultaneous negative shift in $\wilson[NP]{9}$ and
\christoph{$\wilson{T}$}. The prediction of \christoph{${\cal B}(B\to K \bar\mu\mu)$} is
essentially insensitive to $\wilson{T}$ but sensitive to \christoph{$\wilson[NP]{9}$}. A
stronger impact on global fits, however, would \christoph{require a} reduced theory
uncertainty.

The observable \christoph{${\cal B}(B\to K^* \bar\mu\mu)$} shows moderate dependence on
$\wilson{T}$ at least at low $q^2$ and has some impact on the constraints on
tensor couplings as will be discussed in \refsec{sec:results}. At the moment,
theory and experimental uncertainty are of similar size.

$(J_{1c}+J_{2c})$ is sensitive to $\wilson{T}$ in both $q^2$ regimes. At low~$q^2$, 
it is mildly affected by $\wilson[NP]{9}$, whereas at high $q^2$ it is
unaffected. Regarding $(J_{1s}-3J_{2s})$, the situation is reversed: here the
strong dependence on $\wilson{T}$ appears at low $q^2$.  Overall, \christoph{$F_H^\mu$},
$(J_{1c}+J_{2c})$ at \christoph{high} $q^2$, and $(J_{1s}-3J_{2s})$ are sensitive
to $\wilson{T}$ and theoretically very clean around $\wilson{T}=0$.

From the available measurements, \christoph{$F_H^\mu$} at high $q^2$ currently provides the
most stringent constraints on the size of tensor couplings. Moreover, the
dependence on vector couplings is such that $\wilson[NP]{9} \lesssim 0$ leads to
stronger constraints on~$\wilson{T}$ than $\wilson[NP]{9} \approx
0$.

@@

Eventually we also explore the effect of interference with \christoph{NP contributions}
in the vector couplings $\wilson{9,\,9',\,10,\,10'}$ on the bounds 
on tensor and scalar couplings.  For this purpose we include also the branching 
ratio, the lepton forward-backward asymmetry, and the rate CP asymmetry of 
$B\to K^* \bar\mu\mu$ as they provide additional constraints on the real and 
imaginary parts of $\wilson{9,\,9',\,10,\,10'}$. The experimental \christoph{input} of all 
observables entering our fits is listed in \reftab{tab:observables} together with input for
the $B\to K^{(*)}$ form factors. More details on the latter can be found in
\refapp{app:theory:inputs}.

@@

There are no discrepancies between the latest measurements for $\ell = \mu$
(throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ in $B^+ \to K^+
\bar\mu\mu$ and their tiny SM predictions; cf. \reffig{fig:FHvsCT}. Thus our
main objective is to derive constraints on tensor and scalar couplings through
the enhanced sensitivity of both observables to \christoph{these} couplings compared to
vector couplings. For this purpose, we will consider several model-independent
scenarios, progressing from rather restricted to more general ones in order to
asses the effect of cancellations due to interference of various contributions.

For each coupling \christoph{that} we vary in a fit, we remain as general as possible, treat it
as a complex number and use the cartesian parametrization assuming uniform
priors for ease of comparison with previous studies. Specifically, we set
\begin{align}
  \label{eq:wilson-prior}
  \mbox{Re}(\wilson{S,S',P,P',T,T5}) &\in [-1, 1],\nn \mbox{Re}(\wilson{9,9',10,10'}) &\in [-7, 7],
\end{align}
and the same for the imaginary parts. The priors of the nuisance parameters are given in \refapp{app:theory:inputs}.

We start with the scenario of only tensor couplings and see that they are well
constrained by $F_H^\mu$ alone. In a second scenario we consider only scalar
couplings in order to investigate the complementarity of $F_H^\mu$ and $B_s \to
\bar\mu\mu$. Here we find that---for the first time---all complex-valued scalar
couplings can be bounded simultaneously by the combination of both
measurements. Finally we consider as a special scenario the SM augmented by
dimension six operators as an effective theory of new physics below some high
scale $\Lambda_{\rm NP}$ assumed much larger than the typical scale of
electroweak symmetry breaking. In addition, the model contains one scalar
doublet under $SU(2)_L$ as in the SM. For each scenario, we also investigate
interference effects with new physics in vector couplings \christoph{$\wilson{9,9',10,10'}$}. Finally, we conclude
this section with posterior predictions---conditional on all experimental
constraints---of the probable ranges of the not-yet-measured angular observables
\christoph{$J_{6c}$, $(J_{1c}+J_{2c})$ and $(J_{1s} - 3J_{2s}$)}
in $B\to K^*\bar\mu\mu$ and $A_{\Delta\Gamma}$ in $B_s\to\bar\mu\mu$.

@@

In a scenario with only \christoph{complex-valued tensor couplings} $\wilson{T,\, T5}$, the
experimental measurement of $F_H^\mu$ constrains the combination $|\wilson{T}|^2
+ |\wilson{T5}|^2$, up to some small interference of $\wilson{T}$ with vector
couplings $\wilson{7,\,7',\,9,\,9'}$; cf. \refeq{eq:FH-dependence}.  The
according 68\% (95\%) 1D-marginalized probability intervals are listed in the
second column of \reftab{tab:cTT5:1-dimCLs}. From the third column, it is seen
that the constraints become tighter when utilising all observables in
\reftab{tab:observables}, mainly due to the sensitivity of the branching ratio
of $B\to K^{*} \bar\mu\mu$ to tensor couplings (see also
\reffig{fig:FHvsCT}). The latter stronger bounds are driven by the new lattice
results of $B\to K^*$ form factors that predict values above the measured
\christoph{ones}~\cite{Horgan:2013pva}. Since tensor couplings contribute constructively
to ${\cal B}(B\to K^{*}\bar\mu\mu)$, large values are better constrained. In
this scenario with vanishing scalar couplings, current measurements of $A_{\rm
  FB}^\mu(B^+\to K^+\bar\mu\mu)$ barely provide any constraint;
cf.~\refeq{eq:AFB-dependence}.
